---
title: "rmd - module2"
author: "falsanabriamo"
date: "2024-06-14"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is a level 1 header

## R Markdown

### This is a level 3 header

Here is a link to [Google](https://www.google.com/)

Here is a word in **bold** and another word in __bold__.

Here is a word in *italics* and another word in _italics_.

When we compile our document, we are using the `rmarkdown` package.

Here are some example R commands:

```
2+2
mean(c(1,2,3,4,5))
```
```{r prueba}
2+2
mean(c(1,2,3,4,5))

#Cuando no se pone {r}, no se ejecuta el comando, solo cambia el formato de texto
```


Here is an example of a non-numbered list:

* Breakfast
    - food
        + eggs
        + toast
        + bacon
    - drink
        + apple juice
* Lunch
    - taco
* Dinner
    - baked chicken
    - broccoli
    - rice

*Recordar que aquí está la regla de los cuatro espacios: cuatro espacios para una sangría, ocho espacios para dos sangrías...*

Here is an example of a numbered list:

1. Breakfast
    a. food
        i. eggs
        ii. toast
        iii. bacon
    b. drink
        i. apple juice
2. Lunch
    a. taco
3. Dinner
    a. baked chicken
    b. broccoli
    c. rice


Here is an example of a blockquote:

> This is a block quote. This
> paragraph has two lines.
>
> 1. This is a list inside a block quote.
> 2. Second item.


Here is an example of a nested blockquote:

> This is a block quote. This
> paragraph has two lines.
>
> > This text is nested


Here is an example of code in a blockquote:

>     2+2
>     mean(c(1,2,3,4,5))
